psuedocode

### 2020-09-22 Scripts_for_results/16_psuedocode.Rmd
updated main figures; changed suppfig2 to pdf

---
title: "psuedocode"
author: "Spiro Stilianoudakis"
date: "9/6/2020"
output: pdf_document
header-includes:
- \usepackage{stackengine}
- \usepackage{amsmath}
- \usepackage{algorithm2e}
- \usepackage[noend]{algpseudocode}
---

@@

# preciseTAD (CV)

>>>>

---
#title: "psuedocode"
#author: "Spiro Stilianoudakis"
#date: "9/6/2020"
output: pdf_document
header-includes:
- \usepackage{stackengine}
- \usepackage{amsmath}
- \usepackage{algorithm2e}
- \usepackage[noend]{algpseudocode}
---

@@
